Master's Project Journal

### 2019-04-11 thesis/FPGABasedADPLLs.tex
bang bang

\section{Phase Detector}

@@

\section{Loop Filter}
The \acl{LF} in an \ac{ADPLL} can be implemented as a \ac{PI} controller, a circuit that can be implemented in a wide variety of ways, with the exact implementation having little impact on behaviour. The first choice to be made is whether the designer wishes to implement the controller as an \ac{FIR} or \ac{IIR} filter. Both methods will produce a controller that fundamentally behaves the same way, but will have a starkly different implementation. In both cases the filter can be implemented using either fractional or integer representation of the data, depending on the wishes of the designer. Carrying out computations using fractional values may be conceptually easier to understand as the magnitude of individual paths or taps will be independent of another, whereas using integer representations allows for a simpler implementation. If fractional representation is used, it will be done with fixed-point arithmetic as the time complexity of floating point calculations is too great and the potential benefits are inconsequential.

>>>>

\section{Phase Detector}
Three potential \acl{PD} designs will be addressed in this thesis, sign-only detecion with a Bang-Bang Detector, \ac{FPGA} clocked detection using a \ac{FSM} and an emulation of a \ac{TDL} using inverter primitives to create a delay, similarly to the \ac{RO} seen previously. Both designs will have to have a representation for both situations where the generated signal leads and lags the reference signal, and for the magnitude of this difference, a problem most obviously solved by using a signed binary representation of the difference. Most easily implemented in hardware is twos' complement, as operations can be carried out by the same hardware as unsigned arithmetic. The sign convention for phase error assigns the positive values to the situation where the generated signal lags the reference, and vice versa for the leading case. Apart from the Bang-Bang Detector, each design features two blocks, one to determine the sign of the error and a second which estimates the magnitude. These blocks could theoretically be mixed-and-matched, but as they operate on different paradigms no benefit would be obtained.

\subsection{Bang-Bang Detector}
A Bang-Bang Detector is a sign-only detector, thus outputting a phase error just a single bit wide. This can be accomplished using a single flip-flop, with the reference signal acting as the clock, in this case using the rising edge, a design verified by Predrag in his 2011 thesis \cite{redrag}. The generated signal is applied to the $D$ input, thus when a rising edge is seen on the reference the value of the generated signal is held as the $Q$ output until the next rising edge of the reference. If the generated signal has gone high prior to the reference, and leading it, the value of $Q$ will be 1, thereby matching the expected sign behaviour. Trivially it can be seen that the case where the generated signal lags the reference the $Q$ will show 0.

This design is simple but effective, and can even be used without a loop filter, albeit with a very limited oscillator tuning range. This is especially valuable an attribute at an early stage of platform development, as it may be used in order to test that other aspects of the system work as intended. The binary resolution of this detector, however, restricts its usefulness as the \ac{ADPLL} cannot react more quickly to larger phase differences.

\subsection{\acs{FPGA} Clocked Phase Detector}
\subsubsection{State Machine Based Detection}
The easier to implement of the two designs uses a combination of a state machine to determine
\subsubsection{Up-Down Counter}
\subsection{SigNum Detector}
\subsubsection{Sign Detection}
\subsubsection{Tapped Delay Line}

@@

\section{Loop Filter}
The \acl{LF} in an \ac{ADPLL} can be implemented as a \ac{PI} controller, a circuit that can be implemented in a wide variety of ways, with the exact implementation having little impact on behaviour. The first choice to be made is whether the designer wishes to implement the controller as an \ac{FIR} or \ac{IIR} filter. Both methods will produce a controller that fundamentally behaves the same way, but will have a starkly different implementation. In both cases the filter can be implemented using either fractional or integer representation of the data, depending on the wishes of the designer. Carrying out computations using fractional values may be conceptually easier to understand as the magnitude of individual paths or taps will be independent of another, whereas using integer representations allows for a simpler implementation. If fractional representation is used, it will be done with fixed-point arithmetic as the time complexity of floating point calculations is too great and the potential benefits are inconsequential. The \acl{LF} output may be applied directly to the oscillator, or an intermediate calculation done to set a bias point.
